---
title: "International Tourism Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(janitor)
library(DT)
library(forcats)
library(highcharter)
library(scales)

source('data_viz_functions.R')

df <- read_csv('data/International_Tourism_Dataset_Long.csv') %>%
  clean_names()

df_short <- read_csv('data/International_Tourism_Dataset_Short.csv')
```

# Inbound Tourists 

Column {.sidebar data-width=250}
-------------------------------------

"Global tourism suffered its worst year on record in 2020, with international arrivals dropping by 74% according to the latest data from the World Tourism Organization (UNWTO). Destinations worldwide welcomed 1 billion fewer international arrivals in 2020 than in the previous year, due to an unprecedented fall in demand and widespread travel restrictions." -UNWTO 



Column {.tabset .tabset-fade data-width=500}
------------------------------------- 

### Inbound Tourists 2020

```{r}
chloropleth_map(df,
                'International tourism, number of arrivals',
                2020,
                'Which countries recieve the most Tourist',
                'Number of Arriving Tourists')
```

### Inbound Tourists 2019

```{r}
chloropleth_map(df,
                'International tourism, number of arrivals',
                2019,
                'Which countries recieve the most Tourist',
                'Number of Arriving Tourists')
```

### Inbound Tourists 2018

```{r}
chloropleth_map(df,
                'International tourism, number of arrivals',
                2018,
                'Which countries recieve the most Tourist',
                'Number of Arriving Tourists')
```


Column {.tabset .tabset-fade data-width=250}
-----------------------------------------------------------------------

### 2019 Leaders

```{r}
pc_bar_graph(df,
             'International tourism, number of arrivals',
             'prev_year_value',
             'desc')
```

### Aescending

```{r}
pc_bar_graph(df,
             'International tourism, number of arrivals',
             'percent_change',
             'aesc')
```

### Descending

```{r}
pc_bar_graph(df,
             'International tourism, number of arrivals',
             'percent_change',
             'desc')
```

# Outbound Tourists

Column {.sidebar data-width=250}
-------------------------------------

Due to the pandemic, the number of people leaving their countries for tourism drastically decreased. People from countries that normally travel in large numbers like the United States, China, and parts of Europe were forced to stay home. Smaller countries that rely on tourism as an essential source of economic growth suffered significantly because of this.

Column {.tabset .tabset-fade data-width=500}
--------------------------------------

### Outbound Tourists in 2020

```{r}
chloropleth_map(df,
                'International tourism, number of departures',
                2020,
                'Which countries depart the most for tourism',
                'Number of Departing Tourists')
```

### Outbound Tourists in 2019

```{r}
chloropleth_map(df,
                'International tourism, number of departures',
                2019,
                'Which countries depart the most for tourism',
                'Number of Departing Tourists')
```

### Outbound Tourists in 2018

```{r}
chloropleth_map(df,
                'International tourism, number of departures',
                2018,
                'Which countries depart the most for tourism',
                'Number of Departing Tourists')
```

Column {.tabset .tabset-fade data-width=250}
-----------------------------------------------------------------------

### 2019 Leaders

```{r}
pc_bar_graph(df,
             'International tourism, number of departures',
             'prev_year_value',
             'desc')
```

### Aescending

```{r}
pc_bar_graph(df,
             'International tourism, number of departures',
             'percent_change',
             'aesc')
```

### Descending

```{r}
pc_bar_graph(df,
             'International tourism, number of departures',
             'percent_change',
             'desc')
```

# Explore the data

Column {.sidebar data-width=250}
-------------------------------------

Column {.tabset .tabset-fade data-width=375}
-------------------------------------

### Inbound Tourists

```{r}
display_table(df_short, 
              'International tourism, number of arrivals',
              'Blah Blah Blah World Bank Moment')
```

### Outbound Tourists

```{r}
display_table(df_short, 'International tourism, number of departures',
              'Blah Blah Blah World Bank Moment')
```

# References

https://www.unwto.org/tourism-statistics/key-tourism-statistics

https://datacatalog.worldbank.org/

https://www.unwto.org/news/2020-worst-year-in-tourism-history-with-1-billion-fewer-international-arrivals

# About Me

### About this Project

The goal of this dashboard was to show the decrease in global tourism using choropleth maps.

### About Me

My name is Rahim Jutha. I recently finished my undergraduate education at Simon Fraser University studying Statistics and Data Science. I've made this dashboard to develop my R coding skills and to take a look at an interesting data set revolving around global tourism.

https://github.com/rjutha

https://linkedin.com/in/rahim-jutha