---
title: "International Tourism - Exploring the Data"
author: "Rahim Jutha"
date: "2023-06-06"
output: html_document
---

# Description

The goal of this script is to explore the data and develop a story line for the data.

The main components of storytelling with data are:

- Understanding and setting the context
- Exploring multiple angles
- Using compelling visualizations
- Using varied data sources
- Having a consistent narrative

The narrative for this data could be:
- Focusing on a single country
- Looking at which countries rank highest on different metrics

We can answer questions about outbound traffic and inbound traffic related to tourism.

Simple questions we can answer:

- Where are tourists travelling?
- What countries are increasing in popularity? (using historical data)
- Which countries rely on tourism? (percentage of their gdp)
- What is the population in relation to the number of tourists?
- Which tourists spend the most money?
- Is there a correlation between GDP and inbound/outbound tourists?

# Load Packages
```{r}
library(tidyverse)
library(janitor)
library(highcharter)
library(scales)
```

# Load Data
```{r}
df <- read_csv('data/International_Tourism_Dataset_Long.csv') %>%
  clean_names()
# data(worldgeojson, package = "highcharter")
# world_map <- download_map_data(url = "custom/world-robinson-lowres", showinfo = F)
```

# Chloropleth Maps
```{r}
df %>%
  filter(
    indicator == 'International tourism, number of arrivals',
    year == 2005) %>%
  mutate(label = number(value, big.mark = ",")) %>%
  hcmap(
    map = 'custom/world-robinson-lowres',
    download_map_data = TRUE,
    value = "value",
    name = 'Number of Arriving Tourists',
    joinBy = c('iso-a3','iso3c'),
    tooltip = list(
      pointFormat = "{point.country}: {point.label}"
    )
  ) %>%
  hc_colorAxis(
    stops = color_stops(colors = viridisLite::inferno(10, begin = 0.1)),
    max = 10^8,
    labels = list(
      overflow = 'allow'
    )
  ) %>%
  hc_title(text = 'Which countries recieve the most Tourist') %>%
  hc_subtitle(text = 'blah blah blah') %>%
  hc_caption(text = 'blah')
```

```{r}
df %>%
  filter(
    indicator == 'International tourism, number of departures',
    year == 2015) %>%
  mutate(label = number(value, big.mark = ",")) %>%
  hcmap(
    map = 'custom/world-robinson-lowres',
    download_map_data = TRUE,
    value = "value",
    name = 'Number of Departing Tourists',
    joinBy = c('iso-a3','iso3c'),
    tooltip = list(
      pointFormat = "{point.country}: {point.label}"
    )
  ) %>%
  hc_colorAxis(
    stops = color_stops(colors = viridisLite::inferno(10, begin = 0.1)),
    max = 10^8,
    labels = list(
      overflow = 'allow'
    )
  ) %>%
  hc_title(text = 'Which countries depart the most for tourism') %>%
  hc_subtitle(text = 'blah blah blah') %>%
  hc_caption(text = 'blah')
```

```{r}
df %>%
  filter(
    indicator == 'International tourism, number of departures',
    year == 2015) %>%
  mutate(label = number(value, big.mark = ",")) %>%
  hcmap(
    map = 'custom/world-robinson-lowres',
    download_map_data = TRUE,
    value = "value",
    name = 'Number of Departing Tourists',
    joinBy = c('iso-a3','iso3c'),
    tooltip = list(
      pointFormat = "{point.country}: {point.label}"
    )
  ) %>%
  hc_colorAxis(
    stops = color_stops(colors = viridisLite::inferno(10, begin = 0.1)),
    max = 10^8,
    labels = list(
      overflow = 'allow'
    )
  ) %>%
  #hc_title(text = 'Which countries depart the most for tourism') %>%
  hc_subtitle(text = 'blah blah blah') %>%
  hc_caption(text = 'blah')
```


```{r}
df %>%
  filter(
    indicator == 'International tourism, receipts (current US$)',
    year == 2018) %>%
  rename(iso3 = country_code) %>%
  mutate(label = paste('$', number(value, big.mark = ","), 'USD')) %>%
  hcmap(
    map = 'custom/world-robinson-lowres',
    download_map_data = TRUE,
    value = "value",
    name = 'Number of Departing Tourists',
    joinBy = c('iso-a3','iso3'),
    tooltip = list(
      pointFormat = "{point.country_name}: {point.label}"
    ) 
  ) %>%
  hc_colorAxis(
    stops = color_stops(colors = viridisLite::inferno(10, begin = 0.1)),
    max = 25^8,
    labels = list(
      overflow = 'allow'
    )
  ) %>%
  hc_title(text = 'Which countries earn the most from tourism?') %>%
  hc_subtitle(text = 'blah blah blah') %>%
  hc_caption(text = 'blah')
```

# Growth plots
```{r}
df %>%
  filter(
    indicator_name == 'International tourism, number of arrivals') %>%
  mutate(growth_rate = (value - lag(value)) / lag(value),
         label = percent(growth_rate, accuracy = 0.01)) %>%
  filter(country_code == 'USA') %>%
  ggplot(aes(x = year, y = growth_rate)) +
  geom_line()

```

```{r}
df %>%
  filter(
    indicator == 'International tourism, number of arrivals') %>%
  group_by(country) %>%
  mutate(growth_rate = (value - lag(value)) / lag(value),
         label_gr = percent(growth_rate, accuracy = 0.01)) %>%
  mutate(prev_year_value = lag(value)) %>%
  ungroup() %>%
  filter(year == 2020) %>%
  filter(!is.na(growth_rate)) %>%
  arrange(-prev_year_value) %>%
  mutate(label_value = number(value, big.mark = ","),
         label_pyv = number(prev_year_value, big.mark = ",")) %>%
  slice_head(n= 10) %>%
  mutate(country = as_factor(country)) %>%
  hchart(
    'bar',
    hcaes(x = country,
          y = growth_rate),
    color = "#CC4248FF",
    tooltip = list(
      useHTML = TRUE,
      pointFormat = 
        "Growth Rate: {point.label}<br>2019 Tourists: {point.label_pyv}<br> 2020 Tourists: {point.label_value}"
    )
  ) %>%
  hc_xAxis(
    title = list(text = "")
  ) %>%
  hc_yAxis(
    title = list(text = "Growth Rate")
  )
```
```{r}
chloropleth_map(
  df,
  'International tourism, number of arrivals',
  2018,
  'Which countries recieve the most Tourists?')
```