---
title: "International Tourism - Exploring the Data"
author: "Rahim Jutha"
date: "2023-06-06"
output: html_document
---

# Description

The goal of this script is to explore the data and develop a story line for the data.

The main components of storytelling with data are:

- Understanding and setting the context
- Exploring multiple angles
- Using compelling visualizations
- Using varied data sources
- Having a consistent narrative

The narrative for this data could be:
- Focusing on a single country
- Looking at which countries rank highest on different metrics

We can answer questions about outbound traffic and inbound traffic related to tourism.

Simple questions we can answer:

- Where are tourists travelling?
- What countries are increasing in popularity? (using historical data)
- Which countries rely on tourism? (percentage of their gdp)
- What is the population in relation to the number of tourists?
- Which tourists spend the most money?
- Is there a correlation between GDP and inbound/outbound tourists?

# Load Packages
```{r}
library(tidyverse)
library(janitor)
library(highcharter)
```

# Load Data
```{r}
df <- read_csv('data/International_Tourism_Dataset.csv') %>%
  clean_names()
```

# Chloropleth map
```{r}
df %>%
  filter(
    indicator_name == 'International tourism, number of arrivals',
    year == 2016) %>%
  rename(iso3 = country_code) %>%
  hcmap(
    map = 'custom/world-robinson-lowres',
    download_map_data = TRUE,
    value = "value",
    joinBy = c('iso-a3','iso3')
  ) %>%
  hc_colorAxis(
    stops = color_stops(colors = viridisLite::inferno(10, begin = 0.1)),
    type = "logarithmic"
  )

df %>%
  filter(
    indicator_name == 'International tourism, number of arrivals',
    year == 2016) %>%
  arrange(-value) -> x
```